---
title: "February 13"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Aligning multiple structures

How we can read multiple PDB structures from the RCSB PDB for a particular protein:

```{r}
library(bio3d)
ids <- c("1TND_B","1AGR_A","1TAG_A","1GG2_A","1KJY_A","4G5Q_A")  
files <- get.pdb(ids, split = TRUE)
```

The get function will download the requested files. Argument split requests that we want to extract particular chains (WHICH ONES: ). The ids could come from a blast.pdb() search (BLAST.PDB: ).

The following code extracts and aligns the chains we are interested in, and prints a summary of the pdbs object.

```{r}
pdbs <- pdbaln(files, fit = TRUE)
pdbs
```

The pdbaln function superimposes, or fits, all of the structures onto each other using the argument fit = TRUE.

```{r}
#access the first 5 rows and 8 columns
pdbs$ali[1:5, 1:8]

#associated residues numbers 
pdbs$resno[1:5, 1:8]
```

Gap regions are indicated with a - (or NA for pdbs$resno). We can inspect our alignment for gaps using the gap.inspect() function - this provides various indices to obtain an overview of gaps in the alignment object (non-gap columbs, gap containing columns, gaps per row/column).

```{r}
#Inspect alignment for gaps
gaps <- gap.inspect(pdbs$ali)

#Indices of non-gap columns 
head(gaps$f.inds)

#Access non-gap columns
pdbs$ali[, gaps$f.inds]
```

